Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-13 paper/tex/analysis.tex

This analysis is conducted using the \qp\footnote{\url{http://github.com/aimalz/qp/}}\ software package \citep{Malz:qp} for manipulating and calculating metrics of univariate PDFs.
We present the metrics of \pzpdf s that address our goals in the sections below.
Section~\ref{sec:qualmet} outlines aggregate metrics of a catalogue of \pzpdf s, and Section~\ref{sec:CDE_loss} presents a metric of individual \pzpdf s in the absence of true \pzpdf s.
Though the outmoded practices should not be encouraged, those seeking a connection to previous comparison studies will find metrics of redshift point estimate reductions of \pzpdf s in Appendix~\ref{sec:pointmetrics} and metrics of a science-specific summary statistics heuristically derived from \pzpdf s in Appendix~\ref{sec:moments}.

>>>>

This analysis is conducted using the \qp\footnote{\url{http://github.com/aimalz/qp/}}\ software package \citep{Malz:qp} for manipulating and calculating metrics of univariate PDFs.
We present the metrics of \pzpdf s that address our goals in the sections below.
Section~\ref{sec:qualmet} outlines aggregate metrics of a catalogue of \pzpdf s, and Section~\ref{sec:CDE_loss} presents a metric of individual \pzpdf s in the absence of true \pzpdf s.
Those seeking a connection to previous comparison studies will find metrics of redshift point estimate reductions of \pzpdf s in Appendix~\ref{sec:pointmetrics} and metrics of a science-specific summary statistic heuristically derived from \pzpdf s in Appendix~\ref{sec:moments}.

### 2019-11-13 paper/tex/appendix.tex

Many of the codes, including all the model-fitting approaches and \annz, \gpz, \metaphor, and \skynet\ from the data-driven camp, overestimate the redshift density at $z \sim 1.4$.
This behavior is a consequence of the $4000$ \AA break passing through the gap between the $z$ and $y$ filters, which induces a genuine discontinuity in the $z - y$ colour as a function of redshift that can sway the \pzpdf\ estimates in the absence of bluer spectral features.

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
%, particularly for \skynet.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA break passing through the gaps between adjacent filters.
% and logically are more prominent for template-based codes
Even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a degeneracy in the space of colours and redshifts.
% While use of the full information available via $p(z)$ mitigates their impact, a full understanding of the outlier population is critical for LSST science, particularly in tomographic applications.
%\red{I forget what exactly I was trying to say here, if someone else wants to take a crack at this it might be helpful --SJS}
%\scc{may be worth to say that the usage of further bands could mitigate this effect by removing the degeneration  usually induced from emission lines moving across different filters?}

>>>>

Many of the codes, including all the model-fitting approaches and \annz, \gpz, \metaphor, and \skynet\ from the data-driven camp, overestimate the redshift density at $z \sim 1.4$.
This behavior is a consequence of the $4000$ \AA\ break passing through the gap between the $z$ and $y$ filters, which induces a genuine discontinuity in the $z - y$ colour as a function of redshift that can sway the \pzpdf\ estimates in the absence of bluer spectral features.

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withnull_jpg.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
%, particularly for \skynet.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA\ break passing through the gaps between adjacent filters.
% and logically are more prominent for template-based codes
Even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a degeneracy in the space of colours and redshifts.
% While use of the full information available via $p(z)$ mitigates their impact, a full understanding of the outlier population is critical for LSST science, particularly in tomographic applications.
%\red{I forget what exactly I was trying to say here, if someone else wants to take a crack at this it might be helpful --SJS}
%\scc{may be worth to say that the usage of further bands could mitigate this effect by removing the degeneration  usually induced from emission lines moving across different filters?}
